|

### 2016-05-25 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

Aside from the `r nrow(tmp_nona)` unmatched values, `r nrow(the_y)` with the same peptide identification and different spec-evalue, `r nrow(the_z)` of different peptide identification as well different spec-evalues.

>>>>

`r nrow(the_y)` with the same peptide identification and different spec-evalue, `r nrow(the_z)` of different peptide identification as well different spec-evalues (`r nrow(tmp_nona)` of them are unmatched values).
